Litigant Framing Data

### 2022-05-10 data-cleaning/00b-scrape-litigant-text.Rmd
anders

# filter for only briefs that need to be re-pulled
litigant_file_ids <- litigant_file_ids %>% 
  #filter(id %in% c("955405762992", "955404304453", "955405038378", "955401734984", "56699188926", "56701967150","56698341318"))
  filter(id == "861821337076")
```

@@

```{r}
litigant_txt <- litigant_txt %>% 
  mutate(brief_party = ifelse(grepl("\\(feminist\\)", brief, ignore.case=T), 1, 0)) %>% 
  select(case:id, brief_party, txt_full)
```

>>>>

# filter for only briefs that need to be re-pulled
litigant_file_ids <- litigant_file_ids %>% 
  #filter(id %in% c("955405762992", "955404304453", "955405038378", "955401734984", "56699188926", "56701967150","56698341318"))
  #filter(id == "861821337076")
  filter(id == "955826247752")
```

@@

```{r}
litigant_txt <- litigant_txt %>% 
  mutate(brief_party = ifelse(grepl("\\(feminist\\)", brief, ignore.case=T), 1, 0)) %>% 
  mutate(brief_party = ifelse(id %in% c("955405762992", "199347141448", "56697932358", "296368043832"), 1, brief_party)) %>% 
  select(case:id, brief_party, txt_full)
```
